Verifying Demonstrations

### 2020-02-25 paper/distance-bounding.tex
Adds intuition behind DH/DF definition

>>>>

The intuition is that an adversary (malicious, far-away prover) must commit to 
an action: either respond with an own message, which is determined before 
seeing the challenge, or to prompt a nearby prover to respond (with a message 
chosen by the adversary).
Technically, this adversary can do more than \iac{DBDH} adversary normally can.
\Textcite{TREAD} captured this by two dummy sessions \(\sid_{\Commit}\) and 
\(\sid_{\Prompt}\).
The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
m'_{k+1})\) in dummy session \(\sid_{\Commit}\).
If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
session \(\sid_{\Prompt}\), which is the message the nearby prover will send.
